---
title: "opengender_article"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{opengender_article}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(opengender)
```

# Summary

# Statement of Need

## Challenges

## State of the Field

# Approach

# Functionality

## Reference Dictionary Management and Standardization

## Input Standardization

## Fuzzy Matching

## Performance, Reproducibility & Robustness  

## Matching Adjustments

## Uncertainty Estimation and Propagation

## Tidy Syntax

# Using *OpenGender*

# Ongoing Work

This package is part of the *Community Tracking Indicators* project, an initiative to develop standardized indicators that describe the volume and types of open science output systematically over time, using existing open data sources. It functions as a standalone tool in an open pipeline describe a replicable to clean, integrate, code, and analyze multiple bibliometric sources to enable continuous publication of indicators. See [@altman_designing_2022] for a description of the overall pipeline, and preliminary results from this initiative.

# Acknowledgements

Authors gratefully acknowledge support from IMLS (#LG-250130-OLS-21).

# References
